Bayesian MCMC diagnostics and summarization using Tracer 1.6

### 2016-09-26 manuscript/tracer16.tex
small changes and addition of bib

\address{
$^{1}$Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK
$^{2}$Department of Computer Science, University of Auckland, Auckland, NZ\\
$^{3}$Allan Wilson Centre for Molecular Ecology and Evolution, University of Auckland, Auckland, NZ\\
$^{4,5}$Departments of Biomathematics and Human Genetics, David Geffen School of Medicine at UCLA, and \\
$^{6}$Department of Biostatistics, UCLA Fielding School of Public Health, University of California, Los Angeles, USA \\
}

@@

Even users of \textsc{MrBayes} find Tracer handy.

@@

Tracer is a program for analysing the trace files generated by Bayesian MCMC runs (that is, the continuous parameter values sampled from the chain). It can be used to analyse runs of BEAST, MrBayes, LAMARC and possibly other MCMC programs.

Although Tracer can be used with programs other than BEAST, users are strongly advised to join the BEAST mailing-list. This will be used to announce new versions and advise users about bugs and problems.

@@

Estimates - this shows the mean, stdev, confidence intervals and other statistics about the selected parameter. A frequency distribution will also be plotted.
Density - this shows the Bayesian posterior density plot for the selected parameter.
Joint-Marginal - this only appears if exactly 2 parameters are choosen (hold down shift to select multiple parameters). It then plots one against the other to look at their joint-marginal distribution.
Trace - this shows the trace of the parameter against state or generation number. Use this to check mixing, choose a suitable burn-in and look for trends that might suggest problems with convergence.
Multiple parameters can be selected by holding down the shift key. This will overlay the plots for the different parameters allowing comparisons to be made. You can also select multiple trace files as well to compare different runs. If multiple trace files have the same trace names then a "Combined" trace will automatically appear. This can be selected as well as the individual trace files.

>>>>

\address{
$^{1}$Institute of Evolutionary Biology, University of Edinburgh, Edinburgh, UK\\
$^{2}$Department of Computer Science, University of Auckland, Auckland, NZ\\
$^{3}$Centre for Computational Evolution, University of Auckland, Auckland, NZ\\
$^{4,5}$Departments of Biomathematics and Human Genetics, David Geffen School of Medicine at UCLA, and \\
$^{6}$Department of Biostatistics, UCLA Fielding School of Public Health, University of California, Los Angeles, USA \\
}

@@

Even users of \textsc{MrBayes} and \textsc{RevBayes} find Tracer handy.

@@

Tracer is a program for analysing the trace files generated by Bayesian MCMC runs (that is, the continuous parameter values sampled from the chain). It can be used to analyse runs of BEAST \citep{drummond2007beast,drummond2012bayesian}, BEAST2 \citep{bouckaert2014beast2}, MrBayes \citep{ronquist2012mrbayes}, RevBayes \citep{hohna2016revbayes}, LAMARC \citep{kuhner2006lamarc}, Migrate \citep{beerli2006comparison} and possibly other MCMC programs.

Although Tracer can be used with programs other than BEAST, users may find it useful to join the BEAST users mailing list. This is used to announce new versions and advise users about bugs and problems.

@@

Estimates - this shows the mean, stdev, confidence intervals and other statistics about the selected parameter. A frequency distribution will also be plotted.
Density - this shows the Bayesian posterior density plot for the selected parameter.
Joint-Marginal - this only appears if exactly 2 parameters are chosen (hold down shift to select multiple parameters). It then plots one against the other to look at their joint-marginal distribution.
Trace - this shows the trace of the parameter against state or generation number. Use this to check mixing, choose a suitable burn-in and look for trends that might suggest problems with convergence.
Multiple parameters can be selected by holding down the shift key. This will overlay the plots for the different parameters allowing comparisons to be made. You can also select multiple trace files as well to compare different runs. If multiple trace files have the same trace names then a "Combined" trace will automatically appear. This can be selected as well as the individual trace files.
